Sound Automated Synthesis of Digital Controllers

### 2016-10-11 paper/paper.tex
Minor changes

Since the digital control synthesis is performed over a hybrid model, where
the plant displays a continuous behaviour and the controller operates in
both discrete time and state-space, we initially translate the problem into
a single domain which represents a bi-simulation of the original dynamics. 
Given our primary interest in evaluating digital effects in addition to
stability, we have modeled a digital equivalent of the plant by evaluating
the effects of the quantisers (A/D and D/A converters) as time
discretisation elements with quantisation noise.  The resulting closed loop
system is a program loop working over bit-vectors of fixed-point arithmetic
with fixed word length.  The effect of the FWL is included in the model as a
parametric uncertainty which must be taken into account for the correct
synthesis of the controller.

@@

Although the pulse transfer function $G(z)$ represents adequately $G(s)$ domain, the model $G(z)$ may not be accurate and some uncertainties may not be covered by that model. These uncertainties may be parametrically expressed by an additive transfer function $\Delta G(z)$, resulting in a uncertain model $\hat{G}(z)$, such that:
\begin{equation}
\hat{G}(z)=G(z)+\Delta G(z),
\end{equation}
that may be represented by the following transfer function:
\begin{equation}
\hat{G}(z)=\frac{\hat{b}_{0}+\hat{b}_{1}z^{-1}+...+\hat{b}_{M_G}z^{-M_G}}{\hat{a}_{0}+\hat{a}_{1}z^{-1}+...+\hat{a}_{N_G}z^{-N_G}}.
\end{equation}

@@

The ADC and DAC may be abstracted changing the hybrid system in figure~\ref{fig:sampledsystem} to the digital system in figure~\ref{fig:digsystem1} where the parametric uncertainties are represented by $\Delta G_{P}(z)=\mathcal{Z}\left\lbrace{G_{P}(s)}\right\rbrace$ and the entire effect of $\nu_{1}$ and $\nu_{2}$ in the output $Y(z)$ is represented as an additive measurement noise $\nu(z)$.

>>>>

Since the digital control synthesis is performed over a hybrid model, where
the plant displays a continuous behaviour and the controller operates in
both discrete time and state-space, we initially translate the problem into
a single domain which represents a bi-simulation of the original dynamics. 
Given our primary interest in evaluating digital effects in addition to
stability, we have modeled a digital equivalent of the plant by evaluating
the effects of the quantisers (A/D and D/A converters) as time
discretisation elements with quantisation noise.  The resulting closed loop
system is a program loop working over bit-vectors of fixed-point arithmetic
with fixed word length.  \blue{The deterministic effect of the FWL is considered
and quantization errors are included in the model as a additive uncertainty 
which must be taken into account for the correct synthesis of the robust controller
for linear systems with parametric uncertainties.}

@@

Although the pulse transfer function $G(z)$ represents adequately $G(s)$ in z-domain, the model $G(z)$ may not be accurate and some uncertainties may not be covered by that model. These uncertainties may be parametrically expressed by an additive transfer function $\Delta G(z)$, resulting in a uncertain model $\hat{G}(z)$, such that:
\begin{equation}
\hat{G}(z)=G(z)+\Delta G(z),
\end{equation}
that may be represented by the following transfer function:
\begin{equation}
\hat{G}(z)=\frac{\hat{b}_{0}+\hat{b}_{1}z^{-1}+...+\hat{b}_{M_G}z^{-M_G}}{\hat{a}_{0}+\hat{a}_{1}z^{-1}+...+\hat{a}_{N_G}z^{-N_G}}.
\end{equation}

@@

The ADC and DAC may be abstracted changing the hybrid system in figure~\ref{fig:sampledsystem} to the digital system in figure~\ref{fig:digsystem1} where the parametric uncertainties are represented by $\Delta G_{P}(z)=\mathcal{Z}\left\lbrace{G_{P}(s)}\right\rbrace$ and the entire effect of $\nu_{1}$ and $\nu_{2}$ in the output $Y(z)$ is represented as an additive (output) measurement noise $\nu(z)$.
